### 2016-09-28 doc/publications/plos16/plos16.tex
Added more pictures to the scalability seciton

\begin{figure}[tbhp]
\begin{tabular}{ll}
a)& b)\\
\includegraphics[totalheight=6cm]{./figs/nsamples_nvars.png} & 
\includegraphics[totalheight=6cm]{./figs/nvars_nsamples.png} \\
\end{tabular}
\captionof{figure}{{\bf Scalablity of the Wide Random Forest on synthetic datasets with varying number of samples and variables.} 
   {\bf a)} Time in seconds to build 100 trees for differnet mtry fractions. 
   {\bf b)} Number of trees build per hour when using a growing number of CPU cores.}
\label{figure:synth}
\end{figure}

>>>>

\begin{figure}[tbhp]
\begin{tabular}{ll}
a)& b)\\
\includegraphics[totalheight=6cm]{./figs/nvars_nsamples.png} & 
\includegraphics[totalheight=6cm]{./figs/nsamples_nvars.png} \\
\end{tabular}
\captionof{figure}{{\bf Scalablity of the Wide Random Forest on synthetic datasets with varying number of samples and variables.} 
   {\bf a)} Number of trees build per hour when growing number of variables. 
   {\bf b)} Number of trees build per hour when growing number of samples.}
\label{figure:synth}
\end{figure}

\begin{figure}[tbhp]
\begin{tabular}{ll}
a)& b)\\
\includegraphics[totalheight=6cm]{./figs/var_oder.png} & 
\includegraphics[totalheight=6cm]{./figs/var_oob.png} \\
\end{tabular}
\captionof{figure}{{\bf Variable importance (Mean Decrease Gini) and OOB (out of bag) classification error estimate for random forest with 100 trees trained on the synthetic dataset of 2.5M features and 5K samples.} 
   {\bf a)} Variable importance of top 20 variabels normalized to the sum of the linear model coefficients. {\bf Others} represents aggregated importance of variables not present in the linear model.
   {\bf b)} OOB (out of bag) classification error estimate as funtion of mtry fraction.}
\label{figure:synth}
\end{figure}
